---
title: "my_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
This is an introduction to the package packagelab4. 

The next sessions are going to walk you through the package and its functionalities. 

## 1) Aim of the package
This package contains functionalities that help you perform a linear regression given a data set and a formula for 
the regression. The linear regression is as follows: 

<center> $Y = X\beta + \epsilon$  </center>

where Y is the independent variable and X is the matrix of dependent variables including the intercept. 
Using the package you will be able to compute the vector of coefficients and other useful statistics.

## 2) Loading the package
To load the package run the following command:
```{r}
library(packagelab4)
```

## 3) What the package contains
The package contains a reference class called  *linreg*. The class contains six different methods: *new()*, 
*print()*, *plot()*, *resid()*, *pred()*, *coef()*, *summary()*. 
The different methods are going to be explained in the following sections.

## 4) Data set for the examples
From now on we are going to use the in-built data set *iris* to illustrate how the class works. 
To load the data set on to R do as follows:
```{r}
data("iris")
```
The data set has 5 variables and 150 observations.
```{r}
head(iris, 5)
```

## 5) new(), the constructor function
The new() method allows you to create an instance of the class linreg. It takes as input a data frame and a 
formula object related to the variables in the data frame.
```{r}
lin <- linreg$new(Petal.Length ~ Species, iris)
```
*lin* is now an object of the class linreg.

## 6) print()
The print() method displays some useful information about your object of class linreg. In particular, it 
shows the coefficients of the linear regression which are found using the following formula:

<center> $\hat{\beta} = (X^TX)^{-1}X^Ty$ </center>

```{r}
lin$print()
```

## 7) plot()
The plot() method displays two useful graphs for our linear regression: residuals vs fitted and a scale-location plot.

```{r}
lin$plot()
```

## 8) resid()
The method resid() returns the vector of residuals $\hat{e}$ which is computed as follows:

<center> $\hat{e} = \hat{y} - y$ </center>

Here's the code:

```{r}
lin$resid()
```

## 9) pred()
The method pred() returns the predicted values $\hat{y}$ which is computed as follows:

<center> $\hat{y} = X\hat{\beta}$ </center>

Here's the code:

```{r}
lin$pred()
```

## 10) coef()
The method coef() returns the vector of coefficients that are computed as follows:

<center> $\hat{\beta} = (X^TX)^{-1}X^Ty$ </center>

Here's the code:

```{r}
lin$coef()
```

## 11) summary()
The final method is summary() which displays a summary of our regression with all the important statistics:

```{r}
lin$summary()
```
The coefficients are display along with the standard errors and the t values. * , ** and *** are used when the coefficients are statistically different than zero with level 0.01, 0.05 and 0.01 respectively. 
